### 2023-05-03 manuscript.tex
* manuscript.tex: Mention embedding.
* manuscript.tex: Adjust wording.

Attention should be paid to the term \enquote{linear}.  The
interpretation of the term is that phonological transformations apply
to a linear sequence of segments.  This implies the assumption that
segmental phonology, the sort that is dealt with above, is disjoint
from nonsegmental phonology.  This assumption is computationally
unsound, as nonsegmental phonology does not necessarily require
\enquote{nonlinear} accounts.  Another interpretation has to do with
the notion of locality, which is an often misunderstood notion in
theoretical phonology.

@@

The existential introduction reflects the fact that the transformation
only cares about the \textemph{existence} of any term on the tonal
tier that is associated with the input term.

>>>>

Attention should be paid to \enquote{linear}.  One interpretation is
that phonological transformations apply to a linear sequence of
segments.  This implies the assumption that segmental phonology, the
sort that is dealt with above, is disjoint from nonsegmental
phonology.  This assumption is computationally unsound, as
nonsegmental phonology does not necessarily require a
\enquote{nonlinear} account, and conversely segmental phonology may
require one.  Another interpretation has to do with the notion of
locality, which is an often misunderstood notion in theoretical
phonology.

@@

In other words, the linear transformation is \textterm{embedded}.  The
existential introduction reflects the fact that the transformation
only cares about the \textemph{existence} of any term on the tonal
tier that is associated with the input term.
